Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-04 paper/disc20clustering.tex
Comments

\maciek{Algorithm pseudocode comments}
\maciek{This is not good that we need a comment about what $cluster \neq cluster$ means}
\maciek{In pseudocode we need extremely short sentences. $C := singleton components ... $?; $Merge C, C'$ etc}
\maciek{No need to maintain $P_i$'s. Just use one $P$? Or without naming: "move to partition (closeToInit(...))", and remove the partition args from cluster().}
\maciek{Online algorithms should have different pseudocode. Instead of for loop, start with "When a request u,v arrives" (before that it is ok to have init phase just like it is now)}

>>>>

\maciek{Algorithm pseudocode comments}
\maciek{Major thing to discuss: do we even need this? The algorithm is very simple, and the description in the paragraph would be much better. The only way to save it would be to have a general algorithm pseudocode (equivalent to DET), and parametrize it with the repartition procedure. Here, we would say that we choose the closest to initial, and it ALG3 we say that we choose the closest to current.}
\maciek{This is not good that we need a comment about what $cluster \neq cluster$ means}
\maciek{In pseudocode we need extremely short sentences. $C := singleton components ... $?; $Merge C, C'$ etc}
\maciek{No need to maintain $P_i$'s. Just use one $P$? Or without naming: "move to partition (closeToInit(...))", and remove the partition args from cluster().}
\maciek{Online algorithms should have different pseudocode. Instead of for loop, start with "When a request u,v arrives" (before that it is ok to have init phase just like it is now)}
